Turbulence in compact to giant H~II regions

### 2023-04-14 strucfunc_paper.tex
Add data availability statement
Javier changes 2023-04-11

@@

% Will's 2021-12-08 new version of Intro para 4: description of our methodology
In this paper,
we employ archival data from a wide variety of integral field and multi-longslit
spectrographic datasets to analyze spatially resolved \ha{} velocity maps for a sample of
nine \hii{} regions (Figure~\ref{fig:hii-regions}),
ranging in size from \SI{0.5}{pc} to \SI{200}{pc}
and in \ha{} luminosity from \SI{e37}{erg.s^{-1}} to  \SI{e39}{erg.s^{-1}}.
The observations and the physical characteristics of our sample
are described in section~\ref{sec:HIIsample}.
For studying the turbulence we apply a uniform methodology to the analysis of the structure function
by fitting a simple functional form that consists of a power law of slope \(m\)
at small separations,
transitioning to a constant value at separations larger than
an autocorrelation length \(r_0\).
This is described in section~\ref{sec:met}.
We also take into account three observational limitations of the datasets:
the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
the finite map size, \(L_{\text{box}}\);
and a contribution of spatially uncorrelated noise, \(B_0\),
to the observed structure function.
In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
appropriate functional forms for the effects of \(s_0\), \(L_{\text{box}}\) and \(B_0\).
In our fits, we marginalize over these nuisance parameters to obtain robust
credibility limits for the parameters of astrophysical interest:
\(\sigma\pos\), \(r_0\), and \(m\).
The results of these fits are presented in section~\ref{sec:results}.
In section~\ref{sec:discussion} we discuss the relation
of our results to previous studies and the correlations that we find
between the structure function parameters and other properties of
the \hii{} regions in our sample.
%We also discuss the implications of our results for the existence of a
%Kolmogorov-type turbulent energy cascade and the nature of the driving mechanism
%for the velocity fluctuations.
Finally, in section~\ref{sec:conclusions} we present our conclusions.

@@

% \subsubsection{Diameter vs centroid velocity dispersion}

% Other important relationship commonly used in the study of the interstellar medium is the diameter (or size) versus velocity dispersion.
% Table \ref{tab:RestStats} shows this result for our sample in the forth row. 
% This relation presents a significance level \(p > \num{0.05}\) but there are a couple of things worth mentioning.
% Historically this relation is important following the work of \citet{1981MNRAS.194..809L} where he presents it in the context of molecular cloud complexes of many clouds, individual clouds, and clumps, so that size scales are studied over \(\num{0.1} < L < \SI{100}{pc}\) obtaining \(\sigma = 1.10 L ^{0.38}\).

% This relation is interpreted in terms of turbulence, particularly the Kolmogorov model which predicts a index of \num{0.33} so that larger regions presents more turbulence, and smaller regions less turbulence.
% It has been argued that this correlation method is not as powerful as using statistical functions \citep{1984ApJ...277..556S} but it is interesting that the index is consistent within different phases of the interstellar medium.
% We obtain \(\log \sigma\pos = (0.25 \pm 0.17) \log D - (0.2 \pm 0.38)\) which is comparable with \citet{1981MNRAS.194..809L} results.

% As we mentioned in section \ref{sec:L-vs-sigmapos} the fact that this relation holds up to previous investigation gives some certainty that the \(\sigma\pos\) value obtained via the proposed model of the structure function is valid. 
% This implying that the structure function, while not an absolute diagnostic, is a powerful tool in the research of \hii{} regions kinematics.

@@

@@

\section{Degradation of the structure function due to observational limitations}
\label{sec:degr-struct-funct}
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \texttt{make\textunderscore{}extend} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a two-dimensional fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
where \(n = m + 2\) and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).
The maps generated by \texttt{turbustat} are spatially periodic,
but we make them non-periodic by always dividing the full map into at least
four tiles, which are each analyzed separately.

% The artificial fields follows a given power law with a correlation length giving a variance value indicated as true \(\sigma^2\).
% Using this true \(\sigma^2\) we obtain the true \(r_0\) and these values are used as a reference in the experiments to quantify the variations.

\subsection{Finite box effects}
\label{sec:finite-box-effects}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-images}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-finite-box-strucfunc}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\).
    The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
    (b)~Resultant structure functions.
    Colored lines show the average \(B(r)\) over all sub-images,
    while the shaded areas show the standard deviation of \(B(r)\).
  }
  \label{fig:finite-box}
\end{figure}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-effect}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (\(1 - e^{L / 3.6r_0}\)).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

Figure~\ref{fig:finite-box}a shows how we test for finite map effects by taking
a simulated velocity field of size \(512 \times 512\) pixels and iteratively
dividing the full map into \(2 \times 2\) tiles.
On the \(j\)th iteration we have \(N = 4^j\) tiles,
each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
was generated with a correlation length \(r_0 = 16\)~pixels.
We then calculate the individual structure function for each tile and
find the mean and standard deviation for each level of subdivision,
showing the results in Figure~\ref{fig:finite-box}b.
It can be seen that the mean structure functions for each level
of subdivision (shown by colored dots and solid lines)
overlap very closely with one another, apart from deviations
due to edge effects when \(r > L/2\).
On the other hand, there is considerable dispersion between
individual tiles (shown by light colored shading) for the cases
where \(L < r_0\).

We next empirically measure the velocity variance and
apparent correlation length for each tile.
The velocity variance \(\sigma^2\) is found by
directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
while the apparent correlation length \(r_0\)
is found as the separation \(r\) for which \(B(r) = \sigma^2\),
using the tile's own empirically measured structure function and variance.
In Figure~\ref{fig:finite-box-effect}a we show how these
quantities deviate from the ``true'' values
(as measured on the full \(512 \times 512\) map)
as a function of the tile size \(L\).
It can be seen that the true values are successfully recovered
so long as the map size is more than ten times the correlation length,
but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
This can be intuitively understood as due to the fact that a tile that
is small compared with the correlation length will
fail to sample the full range of velocity fluctuations,
leading to an underestimate of \(\sigma^2\).
Then the fact that \(B(r)\) increases with \(r\) in the power law regime
means there will be a concomitant underestimate of \(r_0\).

However, it is possible to do a considerably better job
of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
This is shown in Figure~\ref{fig:finite-box-effect}b, where it can be seen
that the true parameters are reliably recovered so long as \(L > 3 r_0\),
which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
In order for the model fitting to work, the tile size must be large enough
that the structure function begins to show some flattening at the largest scales,
which is why the results are still inaccurate for the smallest values of \(L\)
that sample only the rising power-law portion of \(B(r)\).

\subsection{Effects of seeing}
\label{sec:effects-seeing-struc}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-thumbnails}\\
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-reduction}
  \end{tabular}
  \caption{Effects of seeing on the structure function.
    (a)~Each row shows a different simulated random velocity field
    on a \(256^2\) grid (see text for details).
    The left column shows the original field,
    while the remaining columns show the effects of smoothing by a gaussian kernel
    with RMS width \(s_0\) from 1 to 32 pixels.
    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
    the standard deviation of the unsmoothed map.
    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
    Solid lines with symbols show the average over the 4 maps of
    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
    with a separation of \(2 s_0\) indicated by a large filled circle on each curve.
    Dashed lines shows the empirical fit discussed in the text.
    The dotted line shows the correlation length of the original fields,
    while colored plus symbols show the apparent correlation length of the smoothed fields.
  }
  \label{fig:seeing-reduction}
\end{figure}

@@

Figure~\ref{fig:seeing-reduction}a illustrates how four different
synthetic velocity fields of size \(256\times256\) pixels
and correlation length \(r_0 = \SI{16}{pixels}\)
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \(m = 1.2\)
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.

We find that the following simple analytic function reproduces
these results to within better than 10\%:
\begin{equation}\label{eq:seeingemp2}
S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
\end{equation}
which is shown by dashed lines in Figure \ref{fig:seeing-reduction}b.
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{21}{pc} \).
The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\). 
Above \SI{110}{pc} we see a very disperse downturn  until \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
The seeing (RMS) is \SI{2.1}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and there are no points below this value.
Considering the first point to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{1.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.27} and \num{1.18}, respectively, while our derived value is \num{1.38}.

>>>>

%\usepackage{orcidlink}

@@

% Will's 2021-12-08 new version of Intro para 4: description of our methodology
In this paper,
we employ archival data from a wide variety of integral field and multi-longslit
spectrographic datasets to analyze spatially resolved \ha{} velocity maps for a sample of
nine \hii{} regions (Figure~\ref{fig:hii-regions}),
ranging in size from \SI{0.5}{pc} to \SI{200}{pc}
and in \ha{} luminosity from \SI{e37}{erg.s^{-1}} to  \SI{e39}{erg.s^{-1}}.
The observations and the physical characteristics of our sample
are described in section~\ref{sec:HIIsample}.
For studying the turbulence we apply a uniform methodology to the analysis of the structure function
by fitting a simple functional form that consists of a power law of slope \(m\)
at small separations,
transitioning to a constant value at separations larger than
an autocorrelation length \(r_0\).
This is described in section~\ref{sec:met}.
We also take into account three observational limitations of the datasets:
the finite angular resolution, \(s_0\) (set by pixel spacing or atmospheric seeing);
the finite map size, \(L_{\text{box}}\);
and a contribution of spatially uncorrelated noise, \(B_0\),
to the observed structure function.
In Appendix~\ref{sec:degr-struct-funct} we use simulated velocity maps to derive
appropriate functional forms for the effects of \(s_0\), \(L_{\text{box}}\) and \(B_0\).
In our fits, we marginalize over these nuisance parameters to obtain robust
credibility limits for the parameters of astrophysical interest:
\(\sigma\pos\), \(r_0\), and \(m\).
The results of these fits are presented in section~\ref{sec:results}.
In section~\ref{sec:discussion} we discuss the relation
of our results to previous studies and the correlations that we find
between the structure function parameters and other properties of
the \hii{} regions in our sample.
Finally, in section~\ref{sec:conclusions} we present our conclusions.

@@

@@

\section*{Data availability statement}
\label{sec:data-avail-stat}
All data and accompanying analysis programs used in this paper are available
from the github repository \url{https://github.com/JavGVastro/PhD.Paper}.

@@

\textcolor{red}{\section{Degradation of the structure function due to observational limitations}}
\label{sec:degr-struct-funct}
% Studied in context of \(\Delta\)-variance by \citet{Bensch:2001l}.

To characterize the impact of the finite map size
and the atmospheric seeing on the structure function we perform a series of experiments using artificial turbulent velocity maps.
We quantify how these observational limitations affect the determination of
the structure function parameters, such as
the correlation length \(r_0\) and the velocity field variance \(\sigma\pos^2\). 
The synthetic velocity maps are created using a modified version of the \textcolor{red}{\texttt{make\textunderscore{}3dfield}} command from the \texttt{turbustat} Python library \citep{Koch2019AJ....158....1K},
which creates a \textcolor{red}{three-dimensional} fractional Brownian Motion field
\citep{Miville-Deschenes:2003a}
based on a power-law energy spectrum in wavenumber \(k\), \(E(k) \propto k^{-n}\),
where \textcolor{red}{\(n = m + 3\)} and with random phases. 
Our modification multiplies the energy spectrum by a
low-wavenumber exponential taper:
\(e^{-1 / 2 \pi r_0 k}\).
As a result, the generated fields become uncorrelated at scales larger than \(r_0\)
and the resulting structure function closely approximates our model form
(section~\ref{sec:methods-apply}).

\textcolor{red}{Then we proceed to create a 2D map from collapsing the 3D velocity field so we can take account of projection effects.
We do this by obtaining the 1st-moment map of a PPV (position-position velocity) cube created using the \texttt{make\textunderscore{}ppv} command from \texttt{turbustat}.
To create the PPV cube it was also necessary to create a 3D density field.
The same \texttt{make\textunderscore{}3dfield} command was used to create  (along with the same parameters of the velocity field) a fluctuating density field.
The density fluctuations are interpreted as emissivity fluctuations following as mentioned in section~\ref{sec:constancy-power-law}.}

The maps generated by \texttt{turbustat} are spatially periodic,
but we make them non-periodic by always dividing the full map into at least
four tiles, which are each analyzed separately.

\textcolor{red}{\subsection{Finite box effects}}
\label{sec:finite-box-effects}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-images-ems-fluct_sigE_1}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-3d-finite-box-strucfunc-ems-fluct_sigE_1}
  \end{tabular}
  \caption{Effects of finite box size on the structure function.
    (a)~Construction of simulated turbulent velocity fields of different sizes
    by repeated division of an initial field of size \(512 \times 512\) pixels.
    The \(j\)th level of division yields \(N = 4^j\) fields,
    each of linear size \(L \times L\) where \(L = 2^{9 - j}\).
    The color scale is the same for all maps and it considers \(- 3\) to \(+ 3\) times the standard deviation.
    (b)~Resultant structure functions.
    Colored lines show the average \(B(r)\) over all sub-images,
    while the shaded areas show the standard deviation of \(B(r)\).
  }
  \label{fig:finite-box}
\end{figure}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-3d-finite-box-effect-ems-fluct_sigE_1}
    \\[\bigskipamount]
    (b)\\
    \includegraphics[width=0.95\linewidth]{Figures/fake-finite-box-fits-ems-fluct_sigE_1}
  \end{tabular}
  \caption{
    Reduction of apparent velocity variance and correlation length
    due to finite box size.
    (a)~Empirical measurements of \(\sigma^2\) and \(r_0\).
    Colored dots show mean results from different simulated velocity fields,
    with different power law slopes.
    Colored shading shows the inter-quartile range over the different sub-images.
    The dashed line is an approximate analytic fit to these results
    (\textcolor{red}{\(1 - e^{L / 4.0r_0}\)}).
    (b)~Determination of \(\sigma^2\) and \(r_0\) from fitting the model
    of equation~\eqref{eq:new-correlation-form}.
    Colored dots are mean results from different simulated velocity fields,
    while the dashed line is the same as in (a).
  }
  \label{fig:finite-box-effect}
\end{figure}

\textcolor{red}{Figure~\ref{fig:finite-box}a} shows how we test for finite map effects by taking
a simulated \textcolor{red}{1st moment map of} size \(512 \times 512\) pixels and iteratively
dividing the full map into \(2 \times 2\) tiles.
On the \(j\)th iteration we have \(N = 4^j\) tiles,
each of size \(L \times L \) pixels with \(L = 2^{9 - j}\).
The figure shows the result for \(j = 1\), 2, 3, and 4, in which the full map
was generated with a correlation length \textcolor{red}{\(r_0 = 32\)~pixels}.
We then calculate the individual structure function for each tile and
find the mean and standard deviation for each level of subdivision,
showing the results in \textcolor{red}{Figure~\ref{fig:finite-box}b}.
It can be seen that the mean structure functions for each level
of subdivision (shown by colored dots and solid lines)
overlap very closely with one another, apart from deviations
due to edge effects when \(r > L/2\).
On the other hand, there is considerable dispersion between
individual tiles (shown by light colored shading) for the cases
where \(L < r_0\).

We next empirically measure the velocity variance and
apparent correlation length for each tile.
The velocity variance \(\sigma^2\) is found by
directly averaging over the pixels in the tile using equation~\eqref{eq:sig-pos},
while the apparent correlation length \(r_0\)
is found as the separation \(r\) for which \(B(r) = \sigma^2\),
using the tile's own empirically measured structure function and variance.
In \textcolor{red}{Figure~\ref{fig:finite-box-effect}a} we show how these
quantities deviate from the ``true'' values
(as measured on the full \(512 \times 512\) map)
as a function of the tile size \(L\).
It can be seen that the true values are successfully recovered
so long as the map size is more than ten times the correlation length,
but the apparent values of \(r_0\) and \(\sigma^2\) are smaller than the true values
when \(L < 10 r_0\), increasingly so as \(L\) becomes smaller.
This can be intuitively understood as due to the fact that a tile that
is small compared with the correlation length will
fail to sample the full range of velocity fluctuations,
leading to an underestimate of \(\sigma^2\).
Then the fact that \(B(r)\) increases with \(r\) in the power law regime
means there will be a concomitant underestimate of \(r_0\).

However, it is possible to do a considerably better job
of recovering the true \(\sigma^2\) and \(r_0\) by fitting our
heuristic model structure function of equation~\eqref{eq:model-strucfunc-ideal}.
This is shown in \textcolor{red}{Figure~\ref{fig:finite-box-effect}b}, where it can be seen
that the true parameters are reliably recovered so long as \textcolor{red}{\(L > 5 r_0\)},
which is a roughly \SI{0.5}{dex} improvement over the purely empirical method.
In order for the model fitting to work, the tile size must be large enough
that the structure function begins to show some flattening at the largest scales,
which is why the results are still inaccurate for the smallest values of \(L\)
that sample only the rising power-law portion of \(B(r)\).

\textcolor{red}{\subsection{Effects of seeing}}
\label{sec:effects-seeing-struc}

\begin{figure}
  \begin{tabular}{@{} l @{}}
    (a)\\
    \includegraphics[width=\linewidth]{Figures/fake-3d-seeing-nonp-ems-fluct-thumbnails_sigE_1}\\
    (b)\\
    \includegraphics[width=\linewidth]{Figures/fake-seeing-nonp-3d-ems-fluc_m4-reduction_sigE_1}
  \end{tabular}
  \caption{Effects of seeing on the structure function.
    (a)~Each row shows a different simulated random velocity field
    on a \(256^2\) grid (see text for details).
    The left column shows the original field,
    while the remaining columns show the effects of smoothing by a gaussian kernel
    with RMS width \(s_0\) from 1 to 32 pixels.
    The same color scale is used for all columns, ranging from \(-3\) to \(+3\) times
    the standard deviation of the unsmoothed map.
    (b)~Relative change in the second-order structure function due to the gaussian smoothing.
    Solid lines with symbols show the average over the 4 maps of
    \(B(r, s_0) / B(r, s_0 = 0)\) as a function of separation \(r\),
    with a separation of \textcolor{red}{\(2.6 s_0\)} indicated by a large filled circle on each curve.
    Dashed lines shows the empirical fit discussed in the text.
    The dotted line shows the correlation length of the original fields,
    while colored plus symbols show the apparent correlation length of the smoothed fields.
  }
  \label{fig:seeing-reduction}
\end{figure}

@@

\textcolor{red}{Figure~\ref{fig:seeing-reduction}a} illustrates how four different
synthetic \textcolor{red}{1st-moment maps of} size \(256\times256\) pixels
and correlation length \textcolor{red}{\(r_0 = \SI{32}{pixels}\)}
are affected by progressively broader gaussian seeing,
with RMS width \(s_0 = 1\) to \SI{32}{pixels}.
We calculate the structure function \(B(r)\) for each map and show
in Figure~\ref{fig:seeing-reduction}b the average ratio between
\(B(r)\) and the value in the absence of seeing,
with different colors representing different values of \(s_0\).
Results are shown for a power-law slope of \textcolor{red}{\(m = 1.0\)}
but we find very similar behaviour for other values of \(m\) within the range
seen in our observations.
For small values of \(s_0\), the principle effect is seen at
the smallest separations but the structure function is noticeably depressed
for separations as large as \(r = 10 s_0\).
As \(s_0\) increases to become comparable with \(r_0\),
even the largest separations are significantly affected.
At the same time the apparent correlation length begins to increase,
as indicated by the plus symbols in the figure.

We find that the following simple analytic function reproduces
these results to within better than 10\%:

%\begin{equation}\label{eq:seeingemp2}
%S(r; s_0, r_0) = \frac{e^{-s_0 / r_0}}{1+(2s_0 / r)^{2a}} ,
%\end{equation}

\textcolor{red}{
\begin{equation}\label{eq:seeingemp2}
S(r; s_0, r_0) = 
  \left [
\left (1+\frac{1.25 s_0}{r_0} \right) 
\left(1+ \left (\frac{2.6 s_0}{r} \right) ^{2a} \right)
  \right ]^{-1} ,
\end{equation}
}

which is shown by dashed lines in \textcolor{red}{Figure \ref{fig:seeing-reduction}b}.
The optimum value of the index \(a\) in this equation varies slightly
with the power law slope \(m\) of the true structure function,
but a compromise value of \(a = 0.75\) works tolerably well for \(m = 0.7\) to \(1.3\).
We therefore use this equation to represent the seeing
in our structure function fits (section~\ref{sec:results}),
with \(s_0\) as an additional free parameter for the models.

@@

In the Figure~\ref{fig:strucfunc-fit-ExtraGal}c we show the structure function of NGC 595.
The value of the observed \(\sigma\pos^2 = \SI{44}{km^{2}.s^{-2}}\) is obtained at \(r_0 = \SI{10}{pc} \) (while the derived values from our model are \(\sigma\pos^2 = \SI{53}{km^{2}.s^{-2}}\) and \(r_0 = \SI{11}{pc} \)).
The observed value of \(2\sigma\pos^2\) corresponds to \(r = \SI{21}{pc} \).
The maximum \(B(r)\) value is \SI{104}{km^{2}.s^{-2}} at a separation of \SI{30}{pc}. 
%For NGC 595 we see that the structure function plateau at this maximum \(B(r)\) value, which implies that the observed \(\sigma\pos^2\) is affected by the observational constraints.
Until \(r_0 \sim \SI{55}{pc} \) the structure functions remains closely to the 'true' \(2\sigma\pos^2\), for the largest scale there is a decrease between  \(\SI{55}{pc} < r < \SI{110}{pc} \) where the structure function plateaus at the 'observed' \(2\sigma\pos^2\). 
Above \SI{110}{pc} we see a very disperse downturn  until \SI{54}{km^{2}.s^{-2}} at a separation of \SI{211}{pc}.
The seeing (RMS) is \SI{2.1}{pc} (\(s_0\)=\SI{0.2}{\arcsecond}) and there are no points below this value.
Considering the first point to be valid, which corresponds to \SI{2.5}{km^{2}.s^{-2}} at \(r = \SI{1.05}{pc} \) the slope for \(\sigma\pos^2\) and \(2\sigma\pos^2\) we obtain \num{1.27} and \num{1.18}, respectively, while our derived value is \num{1.38}.
